Word learning at the semantics pragmatics interface

### 2020-04-28 paper/supplementary_material.Rmd
fix typo

[Next](#cognitive-models), we introduce a computational cognitive model (**integration model**) in which we formalize the process of how information sources are integrated. As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the our modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.

>>>>

[Next](#cognitive-models), we introduce a computational cognitive model (**integration model**) in which we formalize the process of how information sources are integrated. As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.
